\documentclass[a4paper,11pt]{letter}

\usepackage[scale=0.70]{geometry}
\usepackage{fontspec}
\usepackage{helvet}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}

\setmainfont{Tex Gyre Heros}

\begin{document}

Dear Eqvilent Hiring Team,

I'm Ivo Maceira, a physicist and programmer looking to transition into quant finance, and I think my research background and experience developing data pipelines are very relevant to Eqvilent's needs in data management and quant research support.

I recently worked in a support role for a data-centric research team. I inherited a messy data management system where:

\begin{itemize}
	\item I implemented a restrictive data validation schema across 5 experimental setups.
	\item I built specialized analysis tools to help experimentalists work with Pandas, in line with your research support and internal tooling needs.
	\item Me and other developers unified the conversion pipelines and deployed it on an in-house server to process 50'000+ experiments monthly.
\end{itemize}

The focus on automation utilities resonates with me since automating my own tasks and workflows is one of my hobbies. I also have extensive experience with Python, NumPy, and Pandas from numerical simulation work in multiple research projects in Physics.

I appreciate your focus on STEM and strong numerical backgrounds, and being able to work remotely from flexible locations is a great perk for me. I'd be glad to discuss how I can contribute to Eqvilent, and I look forward to hearing from you.

Best regards, \\
Ivo Maceira

\end{document}

